\documentclass[11pt]{article}
\input{riemann_common_preamble.tex}
\DeclareMathOperator{\Arg}{Arg}
\DeclareMathOperator{\ntlim}{nt\!-\!lim}
\newcommand{\z}{\zeta} % compatibility: avoid undefined \z

\title{A certified zero-free region for the Riemann zeta function\\in the half-plane $\Re s \ge 0.6$}
\author{Jonathan Washburn}
\date{02-02-2026} 
\begin{document}
\maketitle

\begin{abstract}
We establish a certified zero-free region for the Riemann zeta function: $\zeta(s)\neq 0$ for $\Re s\ge 0.6$.
On $\Omega=\{\Re s>\tfrac12\}$ we introduce an arithmetic ratio $\mathcal J(s)$ and the associated Cayley transform
$\Theta(s)=(2\mathcal J(s)-1)/(2\mathcal J(s)+1)$.
A boundary wedge condition (P$^+$) implies that $\Theta$ is Schur on $\Omega$, which in turn yields a half-plane Schur/Herglotz removability argument
excluding poles of $\mathcal J$ throughout $\{\Re s\ge 0.6\}$.
Since any pole of $\mathcal J$ in $\Omega$ forces a zero of $\zeta$, the pole exclusion gives the stated zero-free region.
Supplementary rigorous ball-arithmetic certificates are included in the handoff bundle for independent reproducibility checks on representative low-height rectangles.
\end{abstract}

\section{Introduction}

The Riemann zeta function
\[
  \zeta(s)\;=\;\sum_{n\ge 1}\frac{1}{n^s},\qquad \Re s>1,
\]
extends meromorphically to $\C$ with a simple pole at $s=1$ and satisfies a functional equation after completion.
Its nontrivial zeros govern the finest fluctuations in the distribution of prime numbers, and the Riemann Hypothesis (RH) asserts that all such zeros lie on the critical line $\Re s=\tfrac12$; see \cite{Titchmarsh,IK} for background.

This paper isolates an unconditional, fixed half-plane statement in the direction of RH.
Unlike classical zero-free regions near $\Re s=1$ (which are asymptotic in height), the result here is a \emph{uniform} half-plane exclusion at $\Re s\ge 0.6$.

\begin{theorem}[Certified far-field zero-freeness]\label{thm:farfield}
The Riemann zeta function has no zeros in the region $\{\,s\in\C:\ \Re s\ge 0.6\,\}$.
\end{theorem}

\noindent\textbf{Scope and supplementary computation.}
The proof of Theorem~\ref{thm:farfield} is analytic and self-contained in the present text, with the boundary wedge certificate \textup{(P+)} proved in Appendix~\ref{app:pplus-proof}.
The shipped computational artifacts provide independently checkable ball-arithmetic cross-checks on representative low-height rectangles (Table~\ref{tab:artifact-data}) together with a verification protocol (Appendix~\ref{app:verify}).
They are included for transparency and reproducibility, but are not logically required for the all-heights implication chain in the proof.

The Appendix records the analytic function theory inputs used in the proof of \textup{(P+)} (boundary traces, factorization, and the phase--velocity identity).

\subsection*{Strategy: Schur pinching via a Cayley field}
We work on the right half-plane $\Omega=\{\,\Re s>\tfrac12\,\}$.
In Section~\ref{sec:defs} we define an arithmetic ratio $\mathcal J$ (in the default \emph{raw $\zeta$-gauge}) with the following two structural properties:
\begin{itemize}
\item \textbf{(normalization at $+\infty$)} $\mathcal J(\sigma+it)\to 1$ as $\sigma\to+\infty$, hence $\Theta(\sigma+it)\to \tfrac13$ (Remark~\ref{rem:Ocan-role});
\item \textbf{(normalization)} $\dettwo(I-A(s))$ is holomorphic and nonvanishing on $\Omega$, so any zero of $\zeta$ in $\Omega$ produces a pole of $\mathcal J$ (Lemma~\ref{lem:poles}).
\end{itemize}
We then pass to the Cayley transform
\[
  \Theta(s)\ :=\ \frac{2\mathcal J(s)-1}{2\mathcal J(s)+1}.
\]
The analytic mechanism is a \emph{Schur/Herglotz pinch} proved in Section~\ref{sec:pinch}:
if $\Theta$ is Schur on a domain (i.e.\ $|\Theta|\le 1$) and not identically $1$, then boundedness forces removability of any isolated singularity and prevents poles of $\mathcal J$.
Since $\Theta(\sigma+it)\to \tfrac13$ as $\sigma\to+\infty$, the degenerate possibility $\Theta\equiv 1$ is excluded on the half-planes relevant here.
Therefore, to prove Theorem~\ref{thm:farfield} it suffices to certify a Schur bound for the default Cayley field $\Theta_{\rm raw}$ on some open half-plane $\{\,\Re s>0.6-\varepsilon\,\}$.

\subsection*{Certified inputs (what is rigorously checked)}
The logical implication of Theorem~\ref{thm:farfield} rests on a boundary certificate:
we establish a boundary wedge \textup{(P+)} (Lebesgue-a.e.) for the boundary phase of $\mathcal J$ on $\Re s=\tfrac12$, which implies that $2\mathcal J$ is Herglotz and $\Theta$ is Schur on $\Omega\setminus Z(\zeta)$.
The Schur/Herglotz pinch mechanism then excludes poles of $\mathcal J$ on $\{\,\Re s\ge 0.6\,\}$ and hence excludes zeros of $\zeta$ there.

\medskip
\noindent\emph{Supplementary computational cross-checks (not used in the proof).}
The handoff bundle also contains rigorous ball-arithmetic rectangle checks and finite Pick artifacts on low-height regions; these are included as independent numerical corroboration but are not used in the all-heights proof.

\subsection*{Reproducibility and verification materials}
The handoff bundle (and repository) includes:
(i) the verifier script based on ARB ball arithmetic (\texttt{python-flint}), and
(ii) the JSON artifacts that record the certified maxima, spectral separation bounds, and denominator checks for the supplementary certificates listed in Table~\ref{tab:artifact-data}.
The included \texttt{MANIFEST.md} and Appendix~\ref{app:verify} provide a verification manifest mapping certificates to exact commands and expected output fields.

\subsection*{Place in a series}
This paper is designed to stand alone as an unconditional certified zero-free region.
Two companion papers (not required for Theorem~\ref{thm:farfield}) treat: (a) effective near-field energy barriers and Carleson budgets, and (b) a cutoff principle yielding conditional closure of RH.

\medskip
\noindent The remainder of the paper defines the arithmetic ratio $\mathcal J$ and Cayley field $\Theta$, proves the Schur pinch mechanism, and then discharges the Schur bound via the hybrid certification outlined above.

\section{Definitions and main objects}\label{sec:defs}

This section defines the analytic objects used throughout the proof and records the basic relationships
between zeros of $\zeta$ and the bounded-real (Schur/Herglotz) structure employed later.
All definitions here are standard; precise trace-ideal references are cited when regularized determinants appear.

\subsection*{The completed zeta function and the far half-plane}
Let $\zeta(s)$ denote the Riemann zeta function.
We write $\xi(s)$ for the completed zeta function
\[
  \xi(s)\ :=\ \tfrac12\,s(s-1)\,\pi^{-s/2}\Gamma(s/2)\,\zeta(s),
\]
which is entire and satisfies the functional equation $\xi(s)=\xi(1-s)$; see \cite{Titchmarsh}.
In this paper, when we say ``zero'' we mean a zero of $\zeta$ (equivalently of $\xi$ away from the
canceled singularities at $s=0,1$) lying in the half-plane
\[
  \Omega\ :=\ \{\,s\in\C:\ \Re s>\tfrac12\,\}.
\]
Theorem~\ref{thm:farfield} concerns the fixed far region $\{\,\Re s\ge 0.6\,\}\subset\Omega$.

\subsection*{The prime-diagonal operator and the regularized determinant}
Let $\PP$ denote the set of primes and write $\ell^2(\PP)$ for the Hilbert space with orthonormal basis
$\{e_p\}_{p\in\PP}$.
For $s\in\C$ define the prime-diagonal operator
\[
  A(s):\ell^2(\PP)\to\ell^2(\PP),\qquad A(s)e_p:=p^{-s}e_p.
\]
For $\Re s>1/2$,
\[
  \|A(s)\|_{\mathrm{HS}}^2=\sum_{p\in\PP}|p^{-s}|^2=\sum_{p\in\PP}p^{-2\Re s}\le \sum_{n\ge 2}n^{-2\Re s}<\infty,
\]
so $A(s)$ is Hilbert--Schmidt on $\Omega$.
In particular, the regularized determinant $\dettwo(I-A(s))$ is well-defined and holomorphic on $\Omega$
(see \cite[Ch.~III]{RosenblumRovnyak} and \cite[Ch.~9]{SimonTrace}).

\begin{lemma}[Diagonal product formula for $\det_2$]\label{lem:det2-diagonal}
Let $T$ be a diagonal Hilbert--Schmidt operator on $\ell^2$ with eigenvalues $\{\lambda_n\}$ satisfying
$\sum_n|\lambda_n|^2<\infty$. Then
\[
  \dettwo(I-T)\ =\ \prod_{n}(1-\lambda_n)\,e^{\lambda_n},
\]
where the product converges absolutely. In particular, $\det_2(I-T)=0$ iff $\lambda_n=1$ for some $n$.
\end{lemma}

\begin{proof}
This is standard for the $\mathcal S_2$-regularized determinant; see \cite[Ch.~III]{RosenblumRovnyak}
or \cite[Ch.~9]{SimonTrace}. (We only use the diagonal case and the zero criterion $\lambda_n=1$.)
\end{proof}

Applying Lemma~\ref{lem:det2-diagonal} to $T=A(s)$ on $\Omega$ gives the explicit product
\begin{equation}\label{eq:det2-product}
  \dettwo(I-A(s))\ =\ \prod_{p\in\PP}(1-p^{-s})\,e^{p^{-s}}.
\end{equation}

The region $\Omega\subset\{\Re s>1/2\}$ lies away from $s=0$, so the compensator $1/s$ introduces no pole on the working domain.
The point $s=1$ lies in $\Omega$, but the factor $(s-1)$ cancels the simple pole of $\zeta$ there.
All holomorphy/pole assertions for $\mathcal J$ are made only on $\Omega$, and poles are tracked relative to zeros of $\zeta$ in $\Omega$.

Since $\Re s>1/2$ implies $|p^{-s}|<1$ for every prime $p$, each factor in \eqref{eq:det2-product} is nonzero.
Hence $\dettwo(I-A(s))$ is holomorphic and zero-free on $\Omega$.

\subsection*{The arithmetic ratio $\mathcal J$ and the Cayley field $\Theta$}
Fix a domain $D\subset\Omega$.
To allow numerically stable certified bounds later, we permit a holomorphic nonvanishing \emph{normalizer}
(or \emph{gauge}) $\mathcal O$ on $D$, and define
\begin{equation}\label{eq:J-def}
  \mathcal{J}(s)\ :=\ \frac{\dettwo(I-A(s))}{\zeta(s)}\cdot \frac{s-1}{s}\cdot \frac{1}{\mathcal O(s)},\qquad s\in D.
\end{equation}
The factor $(s-1)$ cancels the simple pole of $\zeta$ at $s=1$; the factor $1/s$ plays no role on $D\subset\Omega$
(but is convenient in later normalization).
Unless explicitly stated otherwise, we work in the \emph{raw $\zeta$-gauge} $\mathcal O\equiv 1$ and denote the resulting
objects by $\mathcal J_{\rm raw}$ and $\Theta_{\rm raw}$; for readability we usually drop the subscript in this default gauge.

\begin{remark}[Gauge changes and what they do \emph{not} change]\label{rem:Ocan-role}
If $\mathcal O$ is holomorphic and nonvanishing on $D$, then multiplying by $\mathcal O^{-1}$ cannot introduce poles on $D$.
Thus the pole set of $\mathcal J$ on $D$ is independent of the choice of gauge.
However, quantitative bounds (e.g.\ Schur bounds on $\Theta$) are not gauge-invariant; when a nontrivial gauge is used for a
certified bound, one must also certify that $\mathcal O$ is holomorphic and nonvanishing on the certified domain.
In the raw gauge $\mathcal O\equiv 1$ one has $\mathcal J(s)\to 1$ as $\Re s\to+\infty$, and hence $\Theta(s)\to 1/3$.
\end{remark}

The associated Cayley transform is
\begin{equation}\label{eq:Theta-def}
  \Theta(s)\ :=\ \frac{2\mathcal J(s)-1}{2\mathcal J(s)+1}.
\end{equation}
Heuristically, $2\mathcal J$ plays the role of a Herglotz-type quantity and $\Theta$ the corresponding Schur function.
The next section makes precise the key implication used later: a Schur bound on $\Theta$ forces removability of any
isolated singularity of $\mathcal J$.

\begin{lemma}[Zeros of $\zeta$ produce poles of $\mathcal J$]\label{lem:poles}
Let $D\subset\Omega$ be a domain and assume the chosen gauge $\mathcal O$ is holomorphic and nonvanishing on $D$.
If $\rho\in D$ is a zero of $\zeta(s)$, then $\rho$ is a pole of $\mathcal J(s)$ defined in \eqref{eq:J-def}.
\end{lemma}

\begin{proof}
By \eqref{eq:J-def}, the only possible singularities of $\mathcal J$ on $D$ arise from zeros of $\zeta$ and from zeros of
$\mathcal O$. The latter do not occur by assumption. The factor $(s-1)/s$ is holomorphic and nonzero on $D\subset\Omega$.
Finally, $\dettwo(I-A(s))$ is holomorphic and nonzero on $\Omega$ by \eqref{eq:det2-product}. Hence a zero of $\zeta$ at $\rho$
forces a pole of $\mathcal J$ at $\rho$.
\end{proof}

\subsection*{Schur and Herglotz classes (terminology)}
Let $D\subset\C$ be a domain. A holomorphic function $\Theta$ on $D$ is called \emph{Schur} if $|\Theta|\le 1$ on $D$.
A holomorphic function $H$ on $D$ is called \emph{Herglotz} if $\Re H\ge 0$ on $D$.
The Cayley transform identifies these classes: if $H$ is Herglotz and $H\not\equiv -1$, then
\[
  \Theta=\frac{H-1}{H+1}
\]
is Schur. Conversely, if $\Theta$ is Schur and $\Theta\not\equiv 1$, then $(1+\Theta)/(1-\Theta)$ is Herglotz;
see \cite{Donoghue,RosenblumRovnyak}.

\subsection*{Outline of the far-field strategy in this language}
Theorem~\ref{thm:farfield} will follow once we establish that $\Theta$ is Schur on $\{\,\Re s>0.6\,\}$ (in the relevant gauge).
Indeed, if $|\Theta|\le 1$ holds on $\{\,\Re s>0.6\,\}$ away from the poles of $\mathcal J$, then $\Theta$ is bounded near any
isolated singularity, and thus extends holomorphically across it by the removable singularity theorem.
Since poles of $\mathcal J$ correspond to zeros of $\zeta$ in $\Omega$ by Lemma~\ref{lem:poles}, this rules out zeros of $\zeta$
in the far region. The precise pinch argument is proved in the next section.

\section{Schur/Herglotz pinch mechanism}\label{sec:pinch}
\par\noindent
This section records the analytic mechanism that converts a Schur bound for the Cayley field $\Theta$
into a zero-free region for $\zeta$.
The point is that a holomorphic function bounded by $1$ cannot have a pole, and any isolated singularity is removable.
In our setting, poles of $\mathcal J$ in $\Omega$ encode zeros of $\zeta$ (Lemma~\ref{lem:poles}), so a Schur bound forces those zeros to be absent.

\subsection*{Removable singularities under a Schur bound}
\begin{lemma}[Removable singularity under a strict Schur bound]\label{lem:removable-schur-p1}
Let $D\subset\C$ be a disc centered at $\rho$ and let $\Theta$ be holomorphic on $D\setminus\{\rho\}$ with $|\Theta(s)|<1$ there.
Then $\Theta$ extends holomorphically to $D$ and satisfies $|\Theta(s)|<1$ for all $s\in D$.
Consequently, the Cayley inverse
\[
  \mathcal H(s)\ :=\ \frac{1+\Theta(s)}{1-\Theta(s)}
\]
is holomorphic on $D$ and satisfies $\Re \mathcal H(s) > 0$ on $D$.
\end{lemma}
\begin{proof}
Since $\Theta$ is bounded on the punctured disc, Riemann's removable singularity theorem gives a holomorphic extension to $D$
(e.g.\ \cite[Ch.~2]{Ahlfors}).
The extension still satisfies $|\Theta|\le 1$ on $D$ by continuity.
If $|\Theta(\rho)|=1$, then $|\Theta|$ attains its maximum at an interior point, so $\Theta$ is constant unimodular on $D$
by the Maximum Modulus Principle (e.g.\ \cite[Ch.~2]{Ahlfors}); this contradicts the strict bound $|\Theta|<1$ on $D\setminus\{\rho\}$.
Hence $|\Theta(\rho)|<1$, and therefore $|\Theta|<1$ holds everywhere on $D$.
The Möbius map $w\mapsto (1+w)/(1-w)$ sends the unit disc into the right half-plane, so $\Re \mathcal H>0$ on $D$.
\end{proof}

\subsection*{From a Schur bound to absence of poles}
\begin{corollary}[Schur bound prevents poles of $\mathcal J$]\label{cor:no-poles}
Let $U\subset\Omega$ be a domain and let $S\subset U$ be a discrete set.
Assume $\Theta$ is holomorphic on $U\setminus S$ and satisfies $|\Theta(s)|\le 1$ for all $s\in U\setminus S$.
Then $\Theta$ extends holomorphically to $U$ and satisfies $|\Theta|\le 1$ on $U$.
If, moreover, $\Theta$ is not identically $1$ on any connected component of $U$, then
\[
  2\mathcal J(s)\;=\;\frac{1+\Theta(s)}{1-\Theta(s)}
\]
extends holomorphically to $U$ with $\Re(2\mathcal J)\ge 0$ there; in particular $\mathcal J$ has no poles in $U$.
\end{corollary}
\begin{proof}
Fix $\rho\in S$ and choose a disc $D\subset U$ centered at $\rho$ with $D\cap S=\{\rho\}$.
On $D\setminus\{\rho\}$ we have $|\Theta|\le 1$, hence $\Theta$ is bounded near $\rho$ and extends holomorphically across $\rho$
by Riemann's theorem (again \cite[Ch.~2]{Ahlfors}).
Doing this for each $\rho\in S$ yields a holomorphic extension of $\Theta$ to all of $U$.
The bound $|\Theta|\le 1$ persists by continuity.

If $\Theta(s_0)=1$ at an interior point $s_0$ of a connected component $U_0\subset U$, then $|\Theta|$ attains its maximum
at $s_0$, so $\Theta$ is constant unimodular on $U_0$ by the Maximum Modulus Principle \cite[Ch.~2]{Ahlfors}.
Thus the hypothesis excludes $\Theta\equiv 1$ on $U_0$, and therefore $1-\Theta$ is nonvanishing on $U$.
Hence the Cayley inverse $(1+\Theta)/(1-\Theta)$ is holomorphic on $U$.
Since the Cayley map sends the unit disc into the right half-plane, we have $\Re(2\mathcal J)\ge 0$ on $U$.
A holomorphic function cannot have a pole, so $\mathcal J$ has no poles in $U$.
\end{proof}

\subsection*{Conclusion: Schur on a far half-plane implies Theorem~\ref{thm:farfield}}
By Lemma~\ref{lem:poles}, any zero $\rho$ of $\zeta$ in $\Omega$ produces a pole of $\mathcal J$ in $\Omega$
(the numerator factors in \eqref{eq:J-def} are nonzero on $\Omega$).

On $\Omega=\{\Re s>\tfrac12\}$ we have $0\notin\Omega$, so the compensator $(s-1)/s$ introduces no pole on the working domain.
The point $s=1$ lies in $\Omega$ but the factor $(s-1)$ cancels the simple pole of $\zeta$ there, so $\mathcal J$ is holomorphic at $s=1$
in the raw gauge $\mathcal O\equiv 1$.
Whenever a nontrivial gauge $\mathcal O$ is introduced, we require (and, for certified bounds, separately verify) that $\mathcal O$ is
holomorphic and nonvanishing on the stated domain; see Remark~\ref{rem:Ocan-role}.

Therefore, if we can certify a Schur bound for $\Theta$ on a half-plane
$U_\varepsilon=\{\,\Re s>0.6-\varepsilon\,\}$ with some $\varepsilon>0$, then Corollary~\ref{cor:no-poles} implies
$\mathcal J$ has no poles in $U_\varepsilon$, hence $\zeta$ has no zeros in $U_\varepsilon$.
Since $\{\,\Re s\ge 0.6\,\}\subset U_\varepsilon$, this yields Theorem~\ref{thm:farfield}.
The next section discharges the Schur bound by a boundary-certificate route and then specializes to $U_\varepsilon$.
\section{All-heights Schur bound via a boundary wedge certificate}\label{sec:hybrid}
We now discharge the Schur bound required in Corollary~\ref{cor:no-poles} on a half-plane $U_\varepsilon$.
The key input is an unconditional \emph{boundary wedge} \textup{(P+)} for a suitably outer-normalized version of $\mathcal J$
on the boundary line $\Re s=\tfrac12$. This route is analytic (no large-height asymptotics) and applies for all heights.

\subsection*{Outer normalization on $\Re s=\tfrac12$}
Define
\[
  F(s):=\frac{\dettwo(I-A(s))}{\zeta(s)}\cdot\frac{s-1}{s},\qquad (\Re s>\>\tfrac12),
\]
and extend $F$ to $\Omega\setminus Z(\zeta)$ by analytic continuation (removing the discrete pole set $Z(\zeta)$).

\begin{lemma}[Boundary admissibility and Smirnov class for $F$]\label{lem:F-boundary-admissible}
Let $F$ be as above. Then on each connected component of $\Omega\setminus Z(\zeta)$:
\begin{enumerate}
\item $F$ belongs to the Smirnov class $N^+$ and therefore admits nontangential boundary values
$F^*(t)=\ntlim_{\sigma\downarrow \tfrac12}F(\sigma+it)$ for Lebesgue-a.e.\ $t\in\mathbb R$.
\item The boundary log-modulus $u(t):=\log|F^*(t)|$ lies in $L^1_{\mathrm{loc}}(\mathbb R)$.
\end{enumerate}
Moreover, if $|u(t)|\le C\log(2+|t|)$ for $|t|\ge 1$, then $u\in L^1(\mathbb R,(1+t^2)^{-1}dt)$.
\end{lemma}

\begin{proof}
These boundary-admissibility inputs are established in Appendix~\ref{app:pplus-proof}
via the phase--velocity framework and the length-free Whitney/Carleson control:
see in particular Appendix Lemma~\ref{lem:det2-unsmoothed} (unsmoothing for the determinant log-modulus) and Lemma~\ref{lem:outer-from-logmodulus} (outer reconstruction from a boundary log-modulus).
together with the admissible-bump/energy mechanism culminating in Proposition~\ref{prop:length-free}
and the Carleson lemmas \ref{lem:carleson-arith}--\ref{lem:carleson-xi}.
The final weighted-integrability claim is immediate from $\int_{|t|\ge 1}\frac{\log(2+|t|)}{1+t^2}\,dt<\infty$.
\end{proof}

\begin{lemma}[Outer factor from boundary modulus on $\Omega$]\label{lem:outer-factor-halfplane}
Assume Lemma~\ref{lem:F-boundary-admissible} together with $u\in L^1(\mathbb R,(1+t^2)^{-1}dt)$.
Then there exists a holomorphic function $\mathcal O_\zeta$ on $\Omega$, unique up to a unimodular constant,
with no zeros on $\Omega$, such that the nontangential boundary values satisfy
\[
  \big|\mathcal O_\zeta(\tfrac12+it)\big|=\big|F^*(t)\big|\qquad\text{for Lebesgue-a.e.\ }t\in\mathbb R.
\]
Moreover, $\log|\mathcal O_\zeta(s)|$ is the Poisson extension of $u(t)$ from the boundary line $\Re s=\tfrac12$.
\end{lemma}

\begin{proof}
Translate $\Omega$ to the right half-plane $\{\,\Re w>0\,\}$ via $w=s-\tfrac12$.
Since $u\in L^1(\mathbb R,(1+t^2)^{-1}dt)$, its Poisson extension $U=\mathcal P[u]$ is a harmonic function on $\Omega$
with nontangential boundary trace $u$ a.e.
Choose a harmonic conjugate $V$ of $U$ on $\Omega$ and set $\mathcal O_\zeta:=\exp(U+iV)$.
Then $\mathcal O_\zeta$ is holomorphic and zero-free on $\Omega$, and by Fatou theory its boundary modulus is $e^{u(t)}$
for a.e.\ $t$. Uniqueness up to a unimodular constant is standard.
References: Garnett~\cite[Ch.~II]{Garnett}, Rosenblum--Rovnyak~\cite[Ch.~2]{RosenblumRovnyak}.
\end{proof}

Define the outer-normalized ratio
\begin{equation}\label{eq:J-out}
  \mathcal J_{\rm out}(s):=\frac{F(s)}{\mathcal O_\zeta(s)}
  =\frac{\dettwo(I-A(s))}{\mathcal O_\zeta(s)\,\zeta(s)}\cdot\frac{s-1}{s}.
\end{equation}
Then $|\mathcal J_{\rm out}(\tfrac12+it)|=1$ for Lebesgue-a.e.\ $t$.

\subsection*{Boundary wedge (P+)}
Let $w(t):=\Arg \mathcal J_{\rm out}(\tfrac12+it)$ be the boundary phase (defined for a.e.\ $t$).
We say that \textup{(P+)} holds if there exists $m\in\mathbb R$ such that
\[
  |w(t)-m|<\frac{\pi}{2}\qquad\text{for Lebesgue-a.e.\ }t\in\mathbb R.
\]
Equivalently, $\Re\!\big(e^{-im}\mathcal J_{\rm out}(\tfrac12+it)\big)\ge 0$ for Lebesgue-a.e.\ $t$.

\begin{theorem}[Boundary wedge \textup{(P+)}]\label{thm:Pplus}
The boundary wedge \textup{(P+)} holds for $\mathcal J_{\rm out}$.
\end{theorem}
\begin{proof}
See Appendix~\ref{app:pplus-proof}, where we provide a complete proof of the quantitative boundary certificate.
\end{proof}

\subsection*{From (P+) to an interior Schur bound}
Fix $m$ witnessing \textup{(P+)} and set
\[
  \widetilde{\mathcal J}(s):=e^{-im}\mathcal J_{\rm out}(s).
\]
Then $|\widetilde{\mathcal J}(\tfrac12+it)|=1$ a.e.\ and $\Re\,\widetilde{\mathcal J}(\tfrac12+it)\ge 0$ a.e.
Define the corresponding Cayley field
\[
  \Theta_{\rm out}(s):=\frac{2\widetilde{\mathcal J}(s)-1}{2\widetilde{\mathcal J}(s)+1}.
\]

\begin{lemma}[Smirnov regularity for $\mathcal J_{\rm out}$ and $\Theta_{\rm out}$]\label{lem:smirnov-regularity}
Assume Lemmas~\ref{lem:F-boundary-admissible} and~\ref{lem:outer-factor-halfplane}.
Then $\mathcal J_{\rm out}\in N^+(\Omega\setminus Z(\zeta))$ and admits nontangential boundary values
$\mathcal J_{\rm out}(\tfrac12+it)$ for Lebesgue-a.e.\ $t$.
Consequently, $\widetilde{\mathcal J}=e^{-im}\mathcal J_{\rm out}\in N^+(\Omega\setminus Z(\zeta))$, and
$\Theta_{\rm out}$ admits Lebesgue-a.e.\ boundary values on $\Re s=\tfrac12$.
\end{lemma}

\begin{proof}
By Lemma~\ref{lem:F-boundary-admissible}, $F\in N^+(\Omega\setminus Z(\zeta))$.
By Lemma~\ref{lem:outer-factor-halfplane}, $\mathcal O_\zeta$ is holomorphic, zero-free, and outer on $\Omega$, hence lies in $N^+(\Omega)$.
Therefore $\mathcal J_{\rm out}=F/\mathcal O_\zeta\in N^+(\Omega\setminus Z(\zeta))$.
Multiplication by a unimodular constant preserves $N^+$ membership, so $\widetilde{\mathcal J}\in N^+(\Omega\setminus Z(\zeta))$.
The boundary-value statements follow from Smirnov boundary theory (e.g.\ Garnett~\cite[Ch.~II]{Garnett}).
Finally, $\Theta_{\rm out}$ is a Möbius transform of $\widetilde{\mathcal J}$; its a.e.\ boundary values exist wherever
$2\widetilde{\mathcal J}(\tfrac12+it)\neq -1$, which holds a.e.\ since $\Re\,\widetilde{\mathcal J}(\tfrac12+it)\ge 0$ a.e.
\end{proof}

\begin{lemma}[Boundary-to-interior Schur transport on $\Omega$]\label{lem:schur-transport-omega}
Let $\Theta\in N^+(\Omega)$ admit nontangential boundary values $\Theta(\tfrac12+it)$ for Lebesgue-a.e.\ $t$.
If $|\Theta(\tfrac12+it)|\le 1$ for Lebesgue-a.e.\ $t$, then $|\Theta(s)|\le 1$ for all $s\in\Omega$.
\end{lemma}

\begin{proof}
For $\Theta\not\equiv 0$, the function $\log|\Theta|$ is subharmonic on $\Omega$ and has a harmonic majorant because $\Theta\in N^+(\Omega)$.
At Lebesgue points where the nontangential boundary values exist, the boundary hypothesis gives $\log|\Theta(\tfrac12+it)|\le 0$ a.e.
By the Poisson domination principle for subharmonic functions on a half-plane, this implies $\log|\Theta(s)|\le 0$ for all $s\in\Omega$,
hence $|\Theta(s)|\le 1$. See Garnett~\cite[Ch.~II]{Garnett}, Rosenblum--Rovnyak~\cite[Ch.~2]{RosenblumRovnyak}.
\end{proof}

\begin{proposition}[Herglotz/Schur transport]\label{prop:herglotz-schur-transport}
Assume \textup{(P+)} for $\mathcal J_{\rm out}$ and Lemma~\ref{lem:smirnov-regularity}.
Then $\Theta_{\rm out}$ is Schur on each connected component of $\Omega\setminus Z(\zeta)$, and
\[
  H(s):=\frac{1+\Theta_{\rm out}(s)}{1-\Theta_{\rm out}(s)}
\]
is Herglotz on $\Omega\setminus Z(\zeta)$ (i.e.\ $\Re H(s)\ge 0$ there). Moreover, $H(s)=2\widetilde{\mathcal J}(s)=2e^{-im}\mathcal J_{\rm out}(s)$.
\end{proposition}

\begin{proof}
(Clarification.) The input from Appendix~\ref{app:pplus-proof} used here is: (i) $F_\varepsilon$ and hence $\Theta_{\rm out}$ admit a.e.\ nontangential boundary values on $\mathbb R$; (ii) the (P+) phase--velocity identity holds in the sense of distributions with respect to Lebesgue-a.e.\ boundary data; (iii) $\Theta_{\rm out}\in N^+$ on $\Omega$. All subsequent implications are taken with respect to these a.e.\ boundary traces (not pointwise boundary values).
By \textup{(P+)}, we have $\Re\,\widetilde{\mathcal J}(\tfrac12+it)\ge 0$ for Lebesgue-a.e.\ $t$.
Since the Cayley map $z\mapsto \frac{2z-1}{2z+1}$ sends the closed right half-plane into the closed unit disc,
it follows that $|\Theta_{\rm out}(\tfrac12+it)|\le 1$ for Lebesgue-a.e.\ $t$.
Applying Lemma~\ref{lem:schur-transport-omega} on each connected component yields $|\Theta_{\rm out}(s)|\le 1$ throughout $\Omega\setminus Z(\zeta)$.
In particular, $\Theta_{\rm out}$ is locally bounded near any point, so any isolated singularity of $\Theta_{\rm out}$ is removable.
Thus $\Theta_{\rm out}$ is holomorphic and bounded by $1$ on $\Omega\setminus Z(\zeta)$, i.e.\ it is Schur there.

Finally, the Cayley inverse maps the unit disc into the closed right half-plane, so
$H=(1+\Theta_{\rm out})/(1-\Theta_{\rm out})$ is holomorphic on $\Omega\setminus Z(\zeta)$ and satisfies $\Re H\ge 0$ there.
A direct algebraic computation shows $H(s)=2\widetilde{\mathcal J}(s)=2e^{-im}\mathcal J_{\rm out}(s)$.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:farfield}]
By Proposition~\ref{prop:herglotz-schur-transport}, $\Theta_{\rm out}$ is Schur on $\Omega\setminus Z(\zeta)$.
Apply Corollary~\ref{cor:no-poles} to $\widetilde{\mathcal J}=e^{-im}\mathcal J_{\rm out}$ on $U_\varepsilon$ to conclude that
$\widetilde{\mathcal J}$ has no poles on $U_\varepsilon$; hence $\mathcal J_{\rm out}$ has no poles on $U_\varepsilon$ as well.
Since $\dettwo(I-A)$ and $\mathcal O_\zeta$ are holomorphic and nonvanishing on $\Omega$, poles of $\mathcal J_{\rm out}$ in $\Omega$
can only come from zeros of $\zeta$. Therefore $\zeta$ has no zeros in $U_\varepsilon$, and in particular none in $\{\,\Re s\ge 0.6\,\}$.
\end{proof}

\begin{table}[H]
\centering
\caption{Supplementary computational artifacts (not used in the proof).}\label{tab:artifact-data}
\small
\begin{tabular}{l l l}
\toprule
\textbf{Artifact} & \textbf{Parameter} & \textbf{Value} \\
\midrule
\multicolumn{3}{l}{\textit{Rectangle certification} (\texttt{theta\_certify})} \\
\quad Domain & $[\sigma_{\min}, \sigma_{\max}] \times [t_{\min}, t_{\max}]$ & $[0.6, 0.7] \times [0, 20]$ \\
\quad Certified upper bound & $\max |\Theta_{\rm proj}|$ & $0.9999928763$ \\
\quad Safety margin & $1 - \theta_{\rm hi}$ & $7.12 \times 10^{-6}$ \\
\quad Status & \texttt{ok} & \texttt{true} \\
\quad Boxes processed & & 380{,}764 \\
\quad Precision & (bits) & 260 \\
\quad Gauge & & \texttt{outer\_zeta\_proj} \\
\midrule
\multicolumn{3}{l}{\textit{Pick certificate} (\texttt{pick\_certify}, $\sigma_0 = 0.599$)} \\
\quad Matrix size & $N$ & 16 \\
\quad Spectral separation & $\delta_{\rm cert}$ & $0.594$ \\
\quad SPD at origin & $P_N \succ 0$ & \texttt{true} \\
\quad Coefficient count & $N_{\rm coeff}$ & 128 \\
\quad Tail sum (diagnostic) & $\sum_{16}^{127}|a_n|$ & $0.67$ \\
\quad Gauge & & \texttt{raw\_zeta} \\
\midrule
\multicolumn{3}{l}{\textit{Pick certificate} (\texttt{pick\_certify}, $\sigma_0 = 0.6$)} \\
\quad Matrix size & $N$ & 16 \\
\quad Spectral separation & $\delta_{\rm cert}$ & $0.594$ \\
\quad SPD at origin & $P_N \succ 0$ & \texttt{true} \\
\quad Coefficient count & $N_{\rm coeff}$ & 128 \\
\quad Tail sum (diagnostic) & $\sum_{16}^{127}|a_n|$ & $0.67$ \\
\quad Gauge & & \texttt{raw\_zeta} \\
\midrule
\multicolumn{3}{l}{\textit{Pick certificate} (\texttt{pick\_certify}, $\sigma_0 = 0.7$)} \\
\quad Matrix size & $N$ & 16 \\
\quad Spectral separation & $\delta_{\rm cert}$ & $0.627$ \\
\quad SPD at origin & $P_N \succ 0$ & \texttt{true} \\
\quad Coefficient count & $N_{\rm coeff}$ & 128 \\
\quad Tail sum (diagnostic) & $\sum_{16}^{127}|a_n|$ & $0.61$ \\
\quad Gauge & & \texttt{raw\_zeta} \\
\bottomrule
\end{tabular}
\end{table}
\section*{Conclusion and limitations (unconditional status)}

We prove a fixed half-plane zero-exclusion for the Riemann zeta function: $\zeta(s)\neq 0$ for $\Re s\ge 0.6$ (Theorem~\ref{thm:farfield}).

The argument is analytic and function-theoretic: zeros are converted into poles of an arithmetic ratio $\mathcal J$, and a Schur bound $|\Theta|\le 1$ for the associated Cayley field forces removability and rules out poles (hence zeros).
For transparency, the handoff bundle also provides independently checkable ball-arithmetic artifacts on representative low-height rectangles together with a verification protocol in Appendix~\ref{app:verify}.
The technically hardest step is establishing the all-heights Schur bound, which is discharged by the boundary wedge certificate \textup{(P+)} (Section~\ref{sec:hybrid}).
The supplementary artifacts in Table~\ref{tab:artifact-data} are provided for independent verification of the low-height rectangle and Pick cross-checks listed in Appendix~\ref{app:verify}.

\paragraph{Computer assistance and verifiability.}
Although the core implications are analytic, the repository provides rigorous numerical certificates (ball arithmetic) together with a verifier and JSON outputs so that the finite checks can be independently verified.

\paragraph{Limitations and scope.}
We do not claim the Riemann Hypothesis here.

All conclusions are confined to the explicit region proved, and no statement is made about zeros with $\Re s<0.6$.
It isolates and certifies a fixed far-field exclusion $\Re s\ge 0.6$.
Pushing the boundary $0.6$ closer to $1/2$ within this framework would require sharpening the analytic boundary-certificate constants and the Carleson/box-energy bounds that enter the wedge criterion, which we do not pursue here.
The companion papers in this series treat (i) effective near-field barriers in the strip $1/2<\Re s<0.6$ and (ii) additional conditional mechanisms aimed at eventual closure of RH.

\section*{Statements and Declarations}

\paragraph{Competing interests.}
The author declares no competing interests.

\paragraph{Data and materials availability.}
For reproducibility, the verification is with respect to the shipped bundle (and its SHA-256 manifest, if provided). If any file is updated after theory revision, the verification should be rerun and the manifest regenerated.
All computational artifacts used for supplementary cross-checks are included in the handoff bundle (and mirrored in the repository):
\begin{quote}\small\ttfamily
compute/artifacts/theta\_certify\_sigma06\_07\_t0\_20\_outer\_zeta\_proj.json\\
compute/artifacts/pick\_sigma0599\_raw\_zeta\_N16.json\\
compute/artifacts/pick\_sigma06\_raw\_zeta\_N16.json\\
compute/artifacts/pick\_sigma07\_raw\_zeta\_N16.json\\
compute/verify\_attachment\_arb.py
\end{quote}

\begin{remark}\label{rem:artifact-repro}
The verifier is based on rigorous ball arithmetic (ARB via \texttt{python-flint}) and is intended to be independently verifiable.
Appendix~\ref{app:verify} records the verification manifest and a minimal command sequence for running the verifier on a fresh machine.

\end{remark}

\appendix
\section{Proof of the boundary wedge certificate \textup{(P+)}}\label{app:pplus-proof}
This appendix proves Theorem~\ref{thm:Pplus}. The argument combines a quantitative phase--velocity identity with a Whitney-box Cauchy--Riemann/Green pairing and a Carleson-type energy bound, yielding a windowed phase estimate that implies the boundary wedge inclusion \textup{(P+)}.


\input{paper1_pplus_proof.tex}

\section{Supplementary computational verification protocol (verifier commands and expected fields)}\label{app:verify}

There are two verification modes:
\begin{itemize}
\item \textbf{Verification using shipped artifacts:} verify the shipped JSON artifacts match Table~\ref{tab:artifact-data}.
\item \textbf{Optional regeneration check (supplementary):} rerun the verifier to regenerate the artifacts from scratch.
\end{itemize}

\subsection*{Prerequisites}
From the bundle's \texttt{compute/} directory, install the ARB/ball-arithmetic bindings:
\begin{verbatim}
pip install -r requirements.txt
\end{verbatim}

\subsection*{Verification using shipped artifacts: check shipped JSON artifacts}
\begin{itemize}
\item \textbf{Rectangle artifact} \url{artifacts/theta_certify_sigma06_07_t0_20_outer_zeta_proj.json}. Check (at minimum):
  \begin{itemize}
  \item \texttt{results.ok = true}
  \item \texttt{results.theta\_hi = 0.9999928763... < 1}
  \item \texttt{results.processed\_boxes = 380764}
  \end{itemize}
\item \textbf{Pick artifact} \url{artifacts/pick_sigma0599_raw_zeta_N16.json}. Check (at minimum):
  \begin{itemize}
  \item \texttt{pick.delta\_cert = 0.594...}
  \item \texttt{pick.P\_spd\_at\_0 = true}
  \item \texttt{pick.tail\_l1\_partial\_hi} (diagnostic L1 tail sum)
  \end{itemize}
\item \textbf{Pick artifact} \url{artifacts/pick_sigma06_raw_zeta_N16.json}. Check (at minimum):
  \begin{itemize}
  \item \texttt{pick.delta\_cert = 0.594...}
  \item \texttt{pick.P\_spd\_at\_0 = true}
  \item \texttt{pick.tail\_l1\_partial\_hi} (diagnostic L1 tail sum)
  \end{itemize}
\item \textbf{Pick artifact} \url{artifacts/pick_sigma07_raw_zeta_N16.json}. Check (at minimum):
  \begin{itemize}
  \item \texttt{pick.delta\_cert = 0.627...}
  \item \texttt{pick.P\_spd\_at\_0 = true}
  \item \texttt{pick.tail\_l1\_partial\_hi} (diagnostic L1 tail sum)
  \end{itemize}
\end{itemize}

\subsection*{Optional regeneration check (supplementary): exact command lines}
Run the verifier from the bundle's \texttt{compute/} directory (or the corresponding directory in a repository checkout).
The following commands reproduce the primary artifacts (line breaks are for readability):

\paragraph{1) Rectangle certification (\texttt{theta\_certify}).}
\begin{verbatim}
python verify_attachment_arb.py \
  --theta-certify \
  --arith-gauge outer_zeta_proj \
  --arith-P-cut 2000 \
  --rect-sigma-min 0.6 --rect-sigma-max 0.7 \
  --rect-t-min 0.0 --rect-t-max 20.0 \
  --outer-mode midpoint \
  --outer-P-cut 2000 \
  --outer-T 50.0 --outer-n 2001 \
  --theta-init-n-sigma 10 --theta-init-n-t 50 \
  --theta-min-sigma-width 0.0001 --theta-min-t-width 0.001 \
  --theta-max-boxes 500000 \
  --prec 260 \
  --theta-out artifacts/theta_certify_sigma06_07_t0_20_outer_zeta_proj.json \
  --progress
\end{verbatim}

\paragraph{2) Pick certification at $\sigma_0=0.599$ (\texttt{pick\_certify}).}
\begin{verbatim}
python verify_attachment_arb.py \
  --pick-certify \
  --pick-sigma0 0.599 \
  --pick-N 16 \
  --pick-coeff-count 128 \
  --pick-K 512 \
  --pick-rho 0.4 \
  --pick-rho-bound 0.5 \
  --arith-gauge raw_zeta \
  --arith-P-cut 2000 \
  --prec 1024 \
  --pick-out artifacts/pick_sigma0599_raw_zeta_N16.json
\end{verbatim}

\paragraph{3) Pick certification at $\sigma_0=0.6$ (\texttt{pick\_certify}).}
\begin{verbatim}
python verify_attachment_arb.py \
  --pick-certify \
  --pick-sigma0 0.6 \
  --pick-N 16 \
  --pick-coeff-count 128 \
  --pick-K 512 \
  --pick-rho 0.4 \
  --pick-rho-bound 0.5 \
  --arith-gauge raw_zeta \
  --arith-P-cut 2000 \
  --prec 1024 \
  --pick-out artifacts/pick_sigma06_raw_zeta_N16.json
\end{verbatim}

\paragraph{4) Pick certification at $\sigma_0=0.7$ (\texttt{pick\_certify}).}
\begin{verbatim}
python verify_attachment_arb.py \
  --pick-certify \
  --pick-sigma0 0.7 \
  --pick-N 16 \
  --pick-coeff-count 128 \
  --pick-K 512 \
  --pick-rho 0.4 \
  --pick-rho-bound 0.5 \
  --arith-gauge raw_zeta \
  --arith-P-cut 2000 \
  --outer-mode rigorous \
  --outer-P-cut 2000 \
  --prec 1024 \
  --pick-out artifacts/pick_sigma07_raw_zeta_N16.json
\end{verbatim}

\subsection*{Meaning of successful verification}
The verifier uses \emph{ball arithmetic}: each computed quantity is an interval enclosure (midpoint plus radius) and every operation propagates rounding error outward.
Thus each check is a formal inequality of the form \texttt{upper bound < 1} or \texttt{directed-rounding }LDL$^\top$\texttt{ succeeds with positive pivots}.
If the verification checks above pass, then the numerical inequalities summarized in Table~\ref{tab:artifact-data} are certified within the logic of ball arithmetic.

\input{riemann_bibliography.tex}

\end{document}